Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-01 demystify.tex
updates

\paragraph{Remind Your Writers} After you submit your application, you should tell your writers about that and let them know they will soon receive an email from the university to submit their letters.  You should also remind them when you submit your application and ask them to submit their letters on time if they haven't done so.

Note that most places only have deadlines for the applicant, but are very flexible with the letter writers.  In many cases your LOR writers are not even given any deadline.  Also, many places do not begin the admission review process right after the deadline and work on application reviews in the next semester (mid-January).

>>>>

\paragraph{Remind Your Writers} After entering your writers' information in the application system, you should tell your writers about that and let them know they will soon receive an email from the university to submit their letters.  You should also remind them when you submit your application and ask them to submit their letters on time if they haven't done so.

Note that most places only have deadlines for the applicant, but are very flexible with the letter writers.  In many cases your LOR writers \emph{are not given any deadline}. For example, the following list several LOR invitation emails I received from various universities in the past few years:

\begin{emphasisbox}
    \footnotesize
    \paragraph{No deadline given} Examples with no deadline given:

    \textbf{Sample 1:}

    .. is applying for admission into the Computer Science (Ph.D.) program in the Graduate School at the University of Massachusetts Amherst and has listed you as a reference.

    \textbf{They have waived their right of access to see your reference.}

    You may submit your reference online via the Graduate Reference Center, which is located at .. Please use the email address and code shown below to log in to submit this reference.

    A timely response is important for this applicant to be favorably considered. Please be aware that the applicant's admission could be contingent on your prompt response.

    \textbf{Sample 2:}

    Dear ..

    .. has requested that you write a letter of recommendation for their Illinois graduate application. We greatly appreciate your feedback on X's ability to succeed in their graduate studies at Illinois.

    In an effort to make this process as easy as possible for you, we offer the ability to upload your recommendation letter online through our secure website. To submit your recommendation, please use the link below. This link is unique to this recommendation and should not be shared or forwarded.

    Thank you!

    \textbf{Sample 3:}

    .. is applying to the University of Nebraska-Lincoln and has named you as a recommender. \textbf{This applicant has waived the right to view your recommendation.}

    Please complete our brief recommendation form (or if necessary, decline to recommend).

    Should you experience any technical difficulties or require assistance with your account, please contact CollegeNET Support.

    Thank you.

    \paragraph{Deadline given} Several examples with a deadline or some date mentioned:

    \textbf{Sample 1:}

    Dear Dr ..

    .. has listed you as a reference in an application to the EECS graduate program at MIT. If you are not .., please ask .. for the correct letter submission information. Please submit your letter here: ..

    The deadline for the applicant is \textbf{Dec 15}; we start the admissions process immediately after that date, so we would appreciate receiving your recommendation by then. The applicant can see if you have submitted a letter, and may remind you.

    Even though the applicant knows the link for submitting a letter, the applicant is unable to read your submitted letter. The https URL ensures that you connect to MIT's graduate admissions server. That server accepts letter submissions, but will not reveal a submitted letter. The link .. provides a bit more information on MIT's approach to collecting letters of requests.

    Thank you!

    \textbf{Sample 2:}

    Dear Recommender,

    The applicant listed below has applied to a graduate program in the School of Computer Science at Carnegie Mellon University and has requested a letter of recommendation from you.

    Applicant: ..

    Click Here if your mail system provides html content or use the URL below to enter your letter of recommendation in PDF form only.

    Your letter of recommendation is due by \textbf{12 p.m. (Noon) EST on December 10, 20XX}. Thank you for taking the time to respond.
\end{emphasisbox}

Also, many places do not begin the admission review process right after the deadline and work on application reviews in the next semester (mid-January).
